\large{\bf Looking forwards and backwards through locally regulated populations }

### 2023-02-15 forwards-and-backwards.tex
tightness now with improved corectness

\begin{definition}[Martingale Problem Characterisation, scaling limit]
    \label{defn:limiting_lookdown_mgale}
    Fix $\alpha \in [0, \infty)$, and define  
    test functions $f$ by 
    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ 
	with $g$ differentiable in $u$, smooth in $x$, satisfying 
$0\leq g(x,u)\leq 1$ and
    such that there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
    Then, define the operator $A$ on such test functions by 
    \begin{align} \begin{split} \label{eqn:limiting_lookdown_generator}
    A f(\lp)
    &=
        f(\lp)  \sum_{(x, u) \in \xi}
        \gamma(x, \eta)
            \frac{
                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
            }{
                g(x, u)
            }
    \\ &\qquad {} +
        f(\lp) \sum_{(x, u) \in \xi}
        2 \alpha \gamma(x, \eta) r(x, \eta \int_u^\infty (g(x, u_1) - 1) du_1
    \\ &\qquad {} +
        f(\lp) \sum_{(x, u) \in \xi}
        \left(
            \alpha \gamma(x, \eta) r(x, \eta) u^2
            -
            \left\{
                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
            \right\} u
        \right)
        \frac{\partial_u g(x, u)}{ g(x,u) }  .
    \end{split} \end{align}
    Write ${\cal C}(\IR^d\times [0,\infty))$ for the point measures on $\IR^d\times [0,\infty)$.
We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\xi_t)_{t \ge 0}$
    is a solution to the $(A, \lp_0)$ martingale problem
    if it has initial distribution $\lp_0$
    and $f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale for all 
test functions $f$
    as defined above.
\end{definition}

@@

    Again, tightness follows from a compact containment condition
    (Lemma~\ref{lem:compact containment lookdown}),
    tightness of one-dimensional distributions,
    and an application of \citet{EK} Theorem~3.9.1.
    Lines of descent can escape to infinite level in finite time,
    and so we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
    i.e., the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
    of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
    and $h \in C_c([0,\infty))$ is continuous with compact support.
    Theorem~3.9.1 of \citet{EK} requires that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
    is tight as a sequence of real-valued c\`adl\`ag processes for all $F$ in a subset
    of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$,
    that is dense with respect to uniform convergence on compact subsets.
    Lemma~\ref{lem:test_fn_tightness} shows that $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
    for any $f: \overline{\IR^d} \times [0,\infty) \to \IR$ with compact support
    in the level direction.
    The functions $\lp \mapsto \langle f, \lp \rangle$
    do not form not a dense subset of $\bar C(\lpmeasures)$,
    but they do separate points and vanish nowhere, so
    by the Stone-Weierstrass theorem, the algebra they generate is dense in $C_0(\lpmeasures)$,
    the continuous functions that vanish at infinity
    (i.e., are less than $\epsilon$ outside of a compact set, for any $\epsilon$).
    Since $C_0(\lpmeasures)$ is dense in $\bar C(\lpmeasures)$
    with respect to uniform convergence on compact subsets,
    it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
    extends to finite sums and products of these processes,
    which is shown in Lemma~\ref{lem:product_tightness}.

@@

Let $C_c^+$ denote the set of nonnegative continuous functions on $\overline{\IR^d} \times [0, \infty)$
for which there exists a $u_f \ge 0$ such that $u > u_f$ implies that $f(x, u) = 0$.
Recall that we are working with the vague topology ``in the level direction'',
so that $m_n \to m$ in $\lpmeasures$ if and only if $\langle f, m_n \rangle \to \langle f, m \rangle$
for all $f \in C_c^+$.
By Theorem~A.23 in \citet{kallenberg1997foundations},
the space $\lpmeasures$ is separable and metrizable,
and $K \subset \lpmeasures$ is relatively compact if and only if
$\sup_{\lp \in K} \langle f, \lp \rangle < \infty$
for any $f \in C_c^+$.
% The compact sets we consider are those with bounded total mass of their spatial projection,
% i.e., of the form
% $$
%     K_M = \left\{
%         \lp \in \lpmeasures \;:\;
%         \sup_{L \ge 1} \frac{1}{L} \lp\left(\overline{\IR^d} \times [0, L]\right) \le M
%     \right\} .
% $$
% These sets are compact 
% because if $\lp \in K_M$ and $f \in C_c^+$ then $\langle f, \lp\rangle \le M u_f \|f\|_\infty$.
Let $\mathcal{H} = \{h_n\}_{n \ge 1}$ be a sequence of
monotone, nonnegative, compactly supported, differentiable functions
on $[0, \infty)$ such that there exist sequences $u_n \to \infty$ and $k_n$ such that
\begin{enumerate}
    \item $h_n(u) > 1$ for $u \le u_n/2$,
    \item $h_n(u) = 0$ for $u \ge u_n$,
    \item $- h_n(u) \le h_n'(u) \le 0$, and
    \item $\max\left( \int_u^\infty h_n(v) dv, \int_u^\infty h_n(v)^2 dv \right) \le k_n h_n(u)$.
\end{enumerate}
For instance, we could take $h_n(u)$ to be a mollified version of $\min(1, e^{-(u-n)})$,
and then $u_n = k_n = n$.
\comment{(or we could just take those functions? they are differentiable almost everywhere.)}
The compact sets we consider are those with uniformly bounded integrals against $\mathcal{H}$,
i.e., of the form
$$
    K_C = \left\{
        \lp \in \lpmeasures \;:\;
        \langle h_n, \lp \rangle \le C_n
        \text{ for all } n \ge 1
    \right\} ,
$$
for some sequence of constants $(C_1, C_2, \ldots)$.
This set is compact because any $f \in C_c^+$ is bounded by a constant multiple of some $h_n$.

\begin{lemma}[Compact containment for $\lp$]
    \label{lem:compact containment lookdown}
    Under Assumptions~\ref{def:model_setup},
    if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$
    \comment{and they are conditionally Poisson},
    for any $T$ and $\delta > 0$ there exists a sequence
    $(C_1, C_2, \ldots)$ of finite constants such that
    \begin{align} \label{eqn:compact eqn lookdown}
    \limsup_{N \to \infty}
    \IP\left\{
        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
        \text{ for some } n \ge 1
    \right\}
    < \delta .
    \end{align}
\end{lemma}

In other words, the processes $\lp^N$ stay in $K_C$ for all $0 \le t \le T$
with uniformly high probability.
We will prove this Lemma using the following one:

\begin{lemma}
    \label{lem:compact containment hn}
    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
    for any $T$, $M$ and $n$ there exists a constant $K_n$ such that
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > M \right\}
    <
    \frac{K_n}{M} .
    $$
\end{lemma}

\begin{proof}[of Lemma~\ref{lem:compact containment lookdown}]
    By a union bound,
    $$ 
    \IP\left\{
        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
        \text{ for some } n \ge 1
    \right\}
    \le
    \sum_{n \ge 1}
    \IP\left\{
        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
    \right\} ,
    $$
    so \eqref{eqn:compact eqn lookdown} follows
    by taking $C_n = 2^{n-1} K_n / \delta$ and using Lemma~\ref{lem:compact containment hn}.
\end{proof}

\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
    \comment{TODO: just give bounds and say this follows
        the proof of Lemma~\ref{lem:eta_compact_containment} exactly, otherwise.
        Or make the basic idea a lemma in the appendix?}
    Let $h_n \in \mathcal{H}$.
    It is evident from the description of the process
    (or, by differentiating in Definition~\ref{defn:lookdown_mgale})
    that
    Applied to $f(x, u) = h_n(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
    \begin{align*}
    \begin{split}
        \langle h_n, \lp_t^N \rangle
        &=
        \langle h_n, \lp_0^N \rangle
        + M^{h_n}_t 
        \\ & \qquad \qquad {}
        +
        \int_0^t
        \big\langle
            2 a^N(x, \eta^N_s) \int_u^N h_n(u_1) du_1
        ,
        \lp_s^N(dx, du) \big \rangle
        ds
        \\ & \qquad \qquad {}
        +
        \int_0^t
        \big\langle
            \left(
                a^N(x, \eta^N_s) u^2
                - b^N(x, \eta^N_s) u
            \right)
            h_n'(u)
        ,
        \lp_s^N(dx, du) \big \rangle
        ds ,
    \end{split}
    \end{align*}
    where $M^{h_n}_t$ is a martingale
    with quadratic variation
    \begin{align*}
        [M^{h_n}]_t
        &=
        \int_0^t
        \langle 2 a^N(x, \eta_s^N) \int_u^N h_n(u_1)^2 du_1
        ,
        \lp_s^N(dx, du) \big \rangle
        ds .
    \end{align*}
    Now, note that $0 \le a^N(x, \eta_x^N) \le C_a$ for some $C_a < \infty$,
    and we have assumed that $\int_u^\infty h_n(u_1) du_1 \le k_n h_n(u)$,
    so that 
    \begin{align*}
        & \int_0^t
        \big\langle
            2 a^N(x, \eta^N_s) \int_u^N h_n(u_1) du_1
        ,
        \lp_s^N(dx, du) \big \rangle
        ds
        \\ & \qquad
        \le
        2 C_a k_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
    \end{align*}
    In the next line, the contribution from $a^N(x, \eta^N_s) u^2 h'(u)$ is nonpositive because
    $a^N \ge 0$ and $h'(u) \le 0$.
    Similarly, since $b^N(x, \eta_x^N) \le C_b$ for some $C_b < \infty$,
    and by assumption
    $- h_n'(u) \le k_n h_n(u)$ and $h_n'(u) = 0$ for $u \ge u_n$,
    and so
    \begin{align*}
        & \int_0^t
        \big\langle
            \left(
                a^N(x, \eta^N_s) u^2
                - b^N(x, \eta^N_s) u
            \right)
            h_n'(u)
        ,
        \lp_s^N(dx, du) \big \rangle
        ds
        \le
        C_b u_n k_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
    \end{align*}
    Putting this together, we have that
    \begin{align} \label{eqn:hn_bound}
        \langle h_n, \lp_t^N \rangle
        &\le
        \langle h_n, \lp_0^N \rangle
        + M^{h_n}_t 
        + (2 C_a + C_b u_n) k_n \int_0^t 
            \langle h_n, \lp_s^N \rangle
        ds .
    \end{align}
    By Gronwall's inequality, with $C = (2 C_a + C_b u_n) k_n$
    \begin{align*}
        \IE\left[ \langle h_n, \lp_t^N \rangle \right]
        &\le
        \IE\left[ \langle h_n, \lp_0^N \rangle \right] e^{Ct} .
    \end{align*}

    Now consider the maximum. By \eqref{eqn:hn_bound},
    \begin{align*}
        \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle
        &\le
        \langle h_n, \lp_0^N \rangle
        + \sup_{0 \le t \le T} M^{h_n}_t 
        + C \int_0^t 
            \sup_{0 \le t \le T} \langle h_n, \lp_s^N \rangle
        ds .
    \end{align*}
    Again since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
    The Burkholder-Davis-Gundy inequality
    tells us that there is a $C'$ such that
    \begin{align*}
    \IE\left[ \sup_{0 \le t \le T} M^{h_n}_t \right]
    & \le
        C'\left( 1 + \IE\left[ [M^{h_n}]_t \right] \right)
    \\ & \le
        C' \left( 1 + \int_0^t \IE\left[
        \langle 2 a^N(x, \eta_s^N) \int_u^N h_n(u_1)^2 du_1
        ,
        \lp_s^N(dx, du) \big \rangle
        \right] ds \right) 
    \\ & \le
        C' \left( 1 + 2 C_a k_n \int_0^t \IE\left[
        \langle h_n, \lp_s^N \big \rangle
        \right] ds \right) 
    \\ & \le 
        C' \left( 1 + C'' e^{Ct} \IE[ \langle h_n, \lp_t^N \rangle ] \right) ,
    \end{align*}
    where $C'' = 2 C_a k_n / C$.
    Therefore, 
    \begin{align*}
        \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle \right]
        &\le
        C' + \IE\left[ \langle h_n, \lp_0^N \rangle \right]( 1 + C'' e^{Ct} )
        + C \int_0^t 
            \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_s^N \rangle \right]
        ds ,
    \end{align*}
    and so once again by Gronwall's inequality, there is a $C'''$ such that
    \begin{align*}
        \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle \right]
        &\le
        C'''(1 + \IE[\langle h_n, \lp_0^N \rangle]) e^{2Ct} ,
    \end{align*}
    and so
    \begin{align*}
        \IP\left\{ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle > K \right\}
        &\le
        \frac{
            C'''(1 + \IE[\langle h_n, \lp_0^N \rangle]) e^{2CT} 
        }{ K } .
    \end{align*}
\end{proof}

@@

\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
    Again, we use the Aldous-Rebolledo criterion.
    Tightness of $\langle f, \lp_t \rangle$ for a fixed $t$
    follows from Lemma~\ref{lem:compact containment hn},
    so we need only prove conditions analogous to
    \eqref{eqn:eta_projections_goal1}
    and \eqref{eqn:eta_projections_goal2}
    applied to the martingale representation
    of equations~\eqref{eqn:f_xi_mgale} and~\eqref{eqn:f_xi_qv}.
    Indeed, the proof follows exactly as the proof of
    Lemma~\ref{lem:eta_projections_tightness},
    except that terms are bounded by constant multiples of $\langle h_n, \xi^N_s \rangle$
    instead of $\langle 1, \eta^N_s \rangle$,
    where $h_n$ is bounded below on $[0, u_*]$.
    \comment{(or we could say that $u_n \ge 2 u_*$)}
    There is only one term that might use explanation,
    which is
    \begin{align*}
        &
        \frac{\theta}{N} \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
        \\ &\qquad
        % = \frac{\theta}{N} (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) \\ &\qquad
        = \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) ,
    \end{align*}
    but this is now clearly bounded by a constant multiple of $h_n(u)$.
\end{proof}

>>>>

\begin{definition}[Martingale Problem Characterisation, scaling limit]
    \label{defn:limiting_lookdown_mgale}
    Fix $\alpha \in [0, \infty)$, and define  
    test functions $f$ by 
    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ 
	with $g$ differentiable in $u$, smooth in $x$, satisfying 
$0\leq g(x,u)\leq 1$ and
    such that there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
    Then, define the operator $A$ on such test functions by 
    \begin{align} \begin{split} \label{eqn:limiting_lookdown_generator}
    A f(\lp)
    &=
        f(\lp)  \sum_{(x, u) \in \xi}
        \gamma(x, \eta)
            \frac{
                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
            }{
                g(x, u)
            }
    \\ &\qquad {} +
        f(\lp) \sum_{(x, u) \in \xi}
        2 \alpha \gamma(x, \eta) r(x, \eta \int_u^\infty (g(x, u_1) - 1) du_1
    \\ &\qquad {} +
        f(\lp) \sum_{(x, u) \in \xi}
        \left(
            \alpha \gamma(x, \eta) r(x, \eta) u^2
            -
            \left\{
                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
            \right\} u
        \right)
        \frac{\partial_u g(x, u)}{ g(x,u) }  .
    \end{split} \end{align}
    Write ${\cal C}(\IR^d\times [0,\infty))$ for the point measures on $\IR^d\times [0,\infty)$.
We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\lp_t)_{t \ge 0}$
    is a solution to the $(A, \lp_0)$ martingale problem
    if it has initial distribution $\lp_0$
    and $f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale for all 
test functions $f$
    as defined above.
\end{definition}

@@

    Again, tightness follows from a compact containment condition,
    tightness of one-dimensional distributions,
    and an application of \citet{EK} Theorem~3.9.1.

    % Lines of descent can escape to infinite level in finite time, and so
    % we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
    \comment{Should this be a separate definition (along the lines of Condition 2.1 in \citet{etheridge/kurtz:2018})?}
    Let $\{h_k\}$ be a separating class of nonnegative functions in $C^1_b([0, \infty))$
    such that
    $\int_0^\infty \int_u^\infty h_k(v) dv du$,
    $\int_0^\infty u^2 |h_k'(u)| du$,
    and $\int_0^\infty h_k(u)^2 du$
    are all finite for all $k$,
    and assume furthermore that $h_0$ is a positive, nonincreasing function 
    that bounds all other $h_k$, i.e., for any $k$,
    there is a $c_k$ such that $h_k(u) \le c_k h_0(u)$ for all $u \ge 0$.
    (For instance, we may take $h_0(u) = e^{-u}$ and the remaining $h_k$
    to be a separating class of $C^1$ functions with compact support.)
    Following \citet{etheridge/kurtz:2018} (see Condition 2.1),
    we endow $\lpmeasures$ with
    the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
    of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
    and $h \in \{h_k\}_{k \ge 0}$.
    This space is completely metrizable,
    and a subset $K \subset \lpmeasures$ is relatively compact if and only if
    $\sup_{\lp \in K} \langle h_k, \lp \rangle < \infty$ for each $k$;
    therefore, compact containment follows from Lemma~\ref{lem:compact containment lookdown}.

    Theorem~3.9.1 of \citet{EK} requires that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
    is tight as a sequence of real-valued c\`adl\`ag processes for all $F$ in a subset
    of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$,
    that is dense with respect to uniform convergence on compact subsets.
    Lemma~\ref{lem:test_fn_tightness} shows that $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
    for any $f: \overline{\IR^d} \times [0,\infty) \to \IR$ with compact support
    in the level direction.
    The functions $\lp \mapsto \langle f, \lp \rangle$
    do not form not a dense subset of $\bar C(\lpmeasures)$,
    but they do separate points and vanish nowhere, so
    by the Stone-Weierstrass theorem, the algebra they generate is dense in $C_0(\lpmeasures)$,
    the continuous functions that vanish at infinity
    (i.e., are less than $\epsilon$ outside of a compact set, for any $\epsilon$).
    Since $C_0(\lpmeasures)$ is dense in $\bar C(\lpmeasures)$
    with respect to uniform convergence on compact subsets,
    it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
    extends to finite sums and products of these processes,
    which is shown in Lemma~\ref{lem:product_tightness}.

@@

\begin{lemma}[Compact containment for $\lp$]
    \label{lem:compact containment lookdown}
    Under Assumptions~\ref{def:model_setup},
    if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$
    \comment{and they are conditionally Uniform with the limit conditionally Poisson},
    for any $T$ and $\delta > 0$ there exists a sequence
    $(C_1, C_2, \ldots)$ of finite constants such that
    \begin{align} \label{eqn:compact eqn lookdown}
    \limsup_{N \to \infty}
    \IP\left\{
        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_n
        \text{ for some } k \ge 1
    \right\}
    < \delta .
    \end{align}
\end{lemma}

In other words, the processes $\lp^N$ stay in 
the compact set
$$
    \left\{
        \lp \in \lpmeasures \;:\;
        \langle h_k, \lp \rangle \le C_k
        \text{ for all } k \ge 1
    \right\} ,
$$
for all $0 \le t \le T$
with uniformly high probability.
We will prove this Lemma using the following one:

\begin{lemma}
    \label{lem:compact containment hn}
    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
    for any $T$ and $k$ there exists a constant $K_k$ such that
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > M \right\}
    <
    \frac{K_k}{M} .
    $$
\end{lemma}

\begin{proof}[of Lemma~\ref{lem:compact containment lookdown}]
    By a union bound,
    $$ 
    \IP\left\{
        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_k
        \text{ for some } k \ge 1
    \right\}
    \le
    \sum_{k \ge 1}
    \IP\left\{
        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_k
    \right\} ,
    $$
    so \eqref{eqn:compact eqn lookdown} follows
    by taking $C_k = 2^{k-1} K_k / \delta$ and using Lemma~\ref{lem:compact containment hn}.
\end{proof}

\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
    \comment{TODO: shorten and make constants have reasonable notation}
    First note that since $h_k(u) \le c_k h_0(u)$ for all $u$,
    so $\langle h_k, \lp_t^N \rangle \le c_k \langle h_0, \lp_t^N \rangle$,
    and so we need only prove the Lemma for $h_0$.
    Henceforth, let $h = h_0$.
    Applied to $f(x, u) = h(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
    \begin{align*}
    \begin{split}
        \langle h, \lp_t^N \rangle
        &=
        \langle h, \lp_0^N \rangle
        + M^{h}_t 
        \\ & \qquad {}
        +
        \int_0^t
        \big\langle
            2 c^N(x, \eta^N_s) \int_u^N h(v) dv
        ,
        \lp_s^N(dx, du) \big \rangle
        ds
        \\ & \qquad \qquad {}
        +
        \int_0^t
        \big\langle
            \left(
                c^N(x, \eta^N_s) u^2
                - b^N(x, \eta^N_s) u
            \right)
            h'(u)
        ,
        \lp_s^N(dx, du) \big \rangle
        ds ,
    \end{split}
    \end{align*}
    where $M^{h}_t$ is a martingale
    with quadratic variation
    \begin{align*}
        [M^{h}]_t
        &=
        \int_0^t
        \langle 2 c^N(x, \eta_s^N) \int_u^N h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        ds .
    \end{align*}
    Now, note that $0 \le c^N(x, \eta_x^N) \le C_a < \infty$
    and $b^N(x, \eta_s^N) \le C_b < \infty$,
    and we have assumed that $h'(u) \le 0$ (since $h_0$ is nonincreasing),
    so we may bound
    \begin{align} \label{eqn:hn_bound},
    \begin{split} 
        \langle h, \lp_t^N \rangle
        &\le
        \langle h, \lp_0^N \rangle
        + M^{h}_t
        \\ & \qquad {}
        +
        \int_0^t
        \big\langle
            2 C_a \int_u^\infty h(v) dv
            + \left( C_a u^2 + C_b u \right) |h'(u)|
        ,
        \lp_s^N(dx, du) \big \rangle
        ds .
    \end{split}
    \end{align}
    Now, since $\lp_t^N$ is conditionally uniform given $\eta_t^N$,
    we know that for appropriate $f$,
    $  \IE[\langle f, \lp^N_t \rangle] = \IE[\langle \widetilde{f}, \eta^N_t \rangle] , $
    where $\widetilde{f}(x) = \int_0^\infty f(x, u) du$.
    By our assumptions on $h=h_0$,
    we know that
    $$
        \int_0^\infty \left( 2 C_a \int_u^\infty h(v) dv
        + \left( C_a u^2 + C_b u \right) |h'(u)| \right) du
        < C
    $$
    for some $C < \infty$, and so
    \begin{align*}
    \begin{split}
        \IE\left[ \langle h, \lp_t^N \rangle \right]
        &\le
        \IE\left[ \langle h, \lp_0^N \rangle \right]
        +
        C
        \int_0^t
        \IE\bigg[
            \big\langle
            1
            ,
            \eta_s^N(dx, du) \big \rangle
        \bigg]
        ds ,
    \end{split}
    \end{align*}
    which we know by Lemma~\ref{lem:eta_f_bound}
    is bounded by $C_0 e^{C_1 t}$ for some other constants $C_0$ and $C_1$.

    Now consider the maximum. By \eqref{eqn:hn_bound},
    \begin{align*}
        \sup_{0 \le t \le T} \langle h, \lp_t^N \rangle
        &\le
        \langle h, \lp_0^N \rangle
        + \sup_{0 \le t \le T} M^{h}_t 
        \\ & \qquad {}
        + \int_0^T 
        \big \langle
            2 C_a \int_u^\infty h(v) dv
            + \left( C_a u^2 + C_b u \right) |h'(u)|
        ,
        \lp_s^N(dx, du) \big \rangle
        ds ,
    \end{align*}
    where there is no supremum before the integral because the integrand is nonnegative.

    Again since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
    The Burkholder-Davis-Gundy inequality
    tells us that there is a $C'$ such that
    \begin{align*}
    \IE\left[ \sup_{0 \le t \le T} M^{h}_t \right]
    & \le
        C'\left( 1 + \IE\left[ [M^{h}]_T \right] \right)
    \\ & \le
        C' \left( 1 + \int_0^T \IE\left[
        \langle 2 c^N(x, \eta_s^N) \int_u^\infty h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        \right] ds \right) 
    \\ & =
        C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
        \int_0^T \IE\left[
            \langle 1 , \lp_s^N(dx, du) \big \rangle
        \right] ds \right)  
    \\ & \le
        C'' e^{C_1 T} ,
    \end{align*}
    for a constant $C''$ which is finite
    by our assumption that $\int_0^\infty h_0(v)^2 dv < \infty$.

    Therefore, 
    \begin{align*}
        \IE\left[ \sup_{0 \le t \le T} \langle h, \lp_t^N \rangle \right]
        &\le
        \IE\left[ \langle h, \lp_0^N \rangle \right]
        + (C'' + C_0 / C_1) e^{C_1 T},
    \end{align*}
    and so
    \begin{align*}
        \IP\left\{ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle > K \right\}
        &\le
        \frac{
            \IE\left[ \langle h, \lp_0^N \rangle \right]
            + (C'' + C_0 / C_1) e^{C_1 T}
        }{ K } .
    \end{align*}
\end{proof}

@@

\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
    Again, we use the Aldous-Rebolledo criterion.
    Tightness of $\langle f, \lp_t \rangle$ for a fixed $t$
    follows from Lemma~\ref{lem:compact containment hn},
    so we need only prove conditions analogous to
    \eqref{eqn:eta_projections_goal1}
    and \eqref{eqn:eta_projections_goal2}
    applied to the martingale representation
    of equations~\eqref{eqn:f_xi_mgale} and~\eqref{eqn:f_xi_qv}.
    Indeed, the proof follows exactly as the proof of
    Lemma~\ref{lem:eta_projections_tightness},
    except that terms are bounded by constant multiples of $\langle h_0, \xi^N_s \rangle$
    instead of $\langle 1, \eta^N_s \rangle$.
    There is only one term that might use explanation,
    which is
    \begin{align*}
        &
        \frac{\theta}{N} \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
        \\ &\qquad
        % = \frac{\theta}{N} (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) \\ &\qquad
        = \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) ,
    \end{align*}
    but this is now bounded as in the proof of Lemma~\ref{lem:eta_f_bound}.
\end{proof}
